Survivable Set Connectivity

### 2015-05-11 draft.tex
drastically changed the algorithm part

\subsection{Analysis}

First, we argue that the cost of the solution found by this algorithm is within polylogarithmic factors of the optimum.

\begin{lemma}[\cite{ssc}]
$\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
\end{lemma}
This shows that if the algorithm has $\Omega(\frac{k}{\log n})$ edge-disjoint paths between each $(S_i, T_i)$ pair, then it is a polylogarithmic approximation.

\begin{proof}
The proof follows the common strategy: we bound the probability that a given edge is included. If the probabability that a given edge is included is bounded by $O(\log^4n(\frac{\log h}{k} + 1))x_e$, then by linearity of expectation, we would show the claim.

Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$. By line $12$ of the algorithm, for an edge $e \in H$, there needs to be some $e' \in E_t$ such that $e \in \text{map}(e')$ and $e' \in E^{v,q}$ for some $v \in V_t$ and $q$. In addition, $v$ needed to have been $q$-marked.

For each $q$ and $v$, $v$ is $q$-marked with probability at most $\frac{4}{2^{-q}}$. In any of the $\tau'$ iterations of the RoundGKR algorithm where $v$ was $q$-marked, an edge is selected with probability $2^{q+1}y_e$. Figure~\ref{fig:roundgkronnode} shows a possible execution when there is some value of flow found when node $v$ has been $q$-marked.

Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
\begin{align}
height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
&= O(\log^3 n) y_{e'} 
\end{align}
This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values.

So we have shown that the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.

So now in order to include some edge $e$ of the graph, we must include some edge $e' \in \text{map}^{-1}(e)$. So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$, and $Y_{e'}$ be the indicator random variable which says that edge $e'$ in the tree is included in some RoundGKR execution. Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
\begin{align}
X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
\end{align}
Because if $e$ is included in the graph, it must have come from some edge in the tree. 
\begin{align}
 \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
        & = \dfrac{O(\log^4 n)\tau}{k} x_e
\end{align}
So now, bounding the optimum, we get
\begin{align}
\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
\end{align}
So when $\tau = O(\log h + k)$, we get our desired approximation.
\end{proof}

Having established that the expected cost is only polylogarithmic away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.

\begin{definition}
For some set of edges $F \subset E$, the sampled tree embedding, $(T, y, \text{map})$ is bad if $F_T = \text{map}^{-1}(F)$ 
\[ \sum_{e' \in F_T} y_{e'} \geq \frac{1}{2} \]
And good otherwise.
\end{definition}

@@

\begin{lemma}[\cite{ssc}]
\label{lem:notbad}
Fix some $F$, or size at most $\dfrac{k}{16 \alpha}$. Then the probability that a sampled tree embedding $(T, y, \text{map})$ from $\mathcal{D}$ is bad is at most $\frac{1}{2}$. 
\end{lemma}

@@

>>>>

\section{Algorithm Analysis}

\subsection{Overview}

We claim that the algorithm finds a solution which has
\begin{itemize}
\item (Claim A) at least $\Omega(\frac{k}{\log n})$ edge disjoint paths between each $(S_i, T_i)$ pair
\item (Claim B) cost within a polylogarithmic factor of the optimum
\end{itemize}

We first prove Claim A, and then using Claim A, we prove Claim B.

\subsection{Claim A}

\begin{definition}
For some set of edges $F \subseteq E$, the sampled tree embedding, $(T, y, \text{map})$ is bad if $F_T = \text{map}^{-1}(F)$ 
\[ \sum_{e' \in F_T} y_{e'} \geq \frac{1}{2} \]
And good otherwise.
\end{definition}

@@

\begin{lemma}[\cite{ssc}]
\label{lem:notbad}
Fix some $F$ of size at most $\dfrac{k}{16 \alpha}$. Then the probability that a sampled tree embedding $(T, y, \text{map})$ from $\mathcal{D}$ is bad is at most $\frac{1}{2}$. 
\end{lemma}

@@

\subsection{Claim B}

\begin{lemma}[\cite{ssc}]
$\textbf{E}[c(H)] = O(\log^4n(\frac{\log h}{k}+1)) * c(x)$, where $c(x) = \sum_e c(e)x_e$. 
\end{lemma}

\begin{proof}
We prove this by bounding the probability that a given edge is included in $H$ by $O(\log^4n(\frac{\log h}{k} + 1))x_e$. The claim then follows by linearity of expectation.

Let $(T = (V_t, E_t), y, \text{map})$ be a Racke tree sampled from $\mathcal{D}$. For an edge $e$ to be included in our output subgraph $H$, there must have been some tree edge $e' \in E_T$ that maps to $e$ (so $e \in \mathrm{map}(e')$) selected to be in $E^{v,q}$ for some vertex $v \in V_t$ and some index $q \in [0,\dots,2\log n]$. For this to occur, $v$ must be $q$-marked, an event that occurs with probability $\frac{4}{2^{-q}}$.

For a given edge $e'$, there are at most $height(T)$ ancestors, which means that there are at most $height(T)$ different vertices $v$ that, if $q$-marked, may lead to $e'$ being included. For each $v$, we must consider all $O(\log n)$ possible values of $q$. For each value of $q$, the probability of being $q$-marked is $\frac{4}{2^{-q}}$. Once the vertex is $q$-marked, we have $\tau'$ trials of the RoundGKR algorithm, where in each trial, there is a $2^{q+1}y_{e'}$ chance of edge $e'$ being included (by construction of the algorithm). Multiplying these probablities together and applying a union bound over all $\tau'$ trials and over all possible values of $q$, we get an upper bound of

\begin{align}
height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 = O(\log^3 n) y_{e'} 
\end{align}

Since a given edge has $height(T)$ ancestors, it will take part in $height(T)$ possible $v$'s which can be $q$-marked. So the probability that an edge $e'$ in the tree is included is at most 
\begin{align}
height(T) \sum_q \frac{4}{2^{-q}} 2^{q+1} y_{e'} \tau' &= height(T) \tau' y_{e'} \sum_q 2 \\
&= O(\log^3 n) y_{e'} 
\end{align}
This is because $height(T) = O(\log n)$, $\tau' = O(\log n)$, and $q$ takes $O(\log n)$ possible values. So the probability that a given edge of the tree is included in a particular sampling of a Racke tree is $O(\log^3 n) y_{e'}$.

So now in order to include some edge $e$ of the graph $G$, we must include some edge $e' \in \text{map}^{-1}(e)$ (recall that this is the set of tree edges which, if selected, result in edge $e$ being included). So let $X_e$ be the indicator random variable which says that edge $e$ is included in $H$, and $Y_{e'}$ be the indicator random variable which says that edge $e'$ in the tree is included in some RoundGKR execution. Above, we argued that $E[Y_{e'}] \leq O(\log^3 n)y_{e'}$.
\begin{align}
X_e \leq \sum_{e' \in \text{map}(e)} Y_{e'}
\end{align}
Because if $e$ is included in the graph, it must have come from some edge in the tree. 
\begin{align}
 \textbf{E}[X_e] &\leq \tau \sum_{e' \in \text{map}^{-1}(e)} O(\log^3 n) y_{e'} \\
        &= O(\log^3 n) \tau \textbf{E}[load(e)] \\
        &= O(\log^3 n) \tau \textbf{E}[rload(e)x_e'] \\
        &\leq O(\log^3 n) \tau \dfrac{4}{k} \alpha x_e\\
        & = \dfrac{O(\log^4 n)\tau}{k} x_e
\end{align}
So now, bounding the optimum, we get
\begin{align}
\textbf{E}[c(H)] &= \sum_{e \in E} c(x_e)\textbf{E}[X_e] \\
                 &\leq \dfrac{O(\log^4 n)\tau}{k} \sum_{e \in E} c(x_e) x_e
\end{align}
So when $\tau = O(\log h + k)$, we get our desired approximation.
\end{proof}

Having established that the expected cost is only a polylogarithmic factor away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$. We will need the following definition.
